A survey of HTTP caching implementations on the open Semantic Web

### 2015-02-21 sanity/paper1.tex
lc endpoint
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1039 43ef1190-90fd-4dd7-a769-d0121f02b80e

In this paper, we study to what extent SPARQL Endpoints, vocabulary
and data publishers support these standards.

@@

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL Endpoints, vocabularies, or other information
resources, by a spider detailed in Appendix~\ref{app:fetcher},
resulting in 7745 requests, done on 2015-01-02. Although this is not a
very large number, we assume that caching headers are usually set on a
per-host basis, if any differences exist, they are likely on different
types, and so the number of hosts is more important than the
number of resources.

This results in an NQuads file per host, which is then loaded into a
Virtuoso-based SPARQL Endpoint for analysis by using the statistics
system R\cite{kn:r} in the following section.

@@

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. On the vertical axis, the size of the boxes
    are determined by the fraction of the types of resources. On the
    horizontal axis the width of the boxes is proportional to the
    total counts, using the same bins as in
    Figure~\ref{fig:hardall}. Yellow boxes denote SPARQL Endpoints,
    green dataset descriptions, blue generic information resources and
    red vocabularies.}
  \label{fig:hardtable}
\end{figure}

@@

We find that only one SPARQL Endpoint yields a heuristic lifetime, on
closer inspection, we find this to be hosted by
Dydra\footnote{http://dydra.com/}. We speculate that this is due to
that few underlying DBMS systems help track modification times in a
way that can be used on a SPARQL result basis.

@@

For SPARQL Endpoints, it is interesting to examine the queries in a
shared proxy, e.g. an institutional cache or a Content
Delivery Network for frequent subpatterns, and prefetch and cache such
intermediate results so that subsequent queries can be answered in
part by the proxy.

>>>>

In this paper, we study to what extent SPARQL endpoints, vocabulary
and data publishers support these standards.

@@

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL endpoints, vocabularies, or other information
resources, by a spider detailed in Appendix~\ref{app:fetcher},
resulting in 7745 requests, done on 2015-01-02. Although this is not a
very large number, we assume that caching headers are usually set on a
per-host basis, if any differences exist, they are likely on different
types, and so the number of hosts is more important than the
number of resources.

This results in an NQuads file per host, which is then loaded into a
Virtuoso-based SPARQL endpoint for analysis by using the statistics
system R\cite{kn:r} in the following section.

@@

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. On the vertical axis, the size of the boxes
    are determined by the fraction of the types of resources. On the
    horizontal axis the width of the boxes is proportional to the
    total counts, using the same bins as in
    Figure~\ref{fig:hardall}. Yellow boxes denote SPARQL endpoints,
    green dataset descriptions, blue generic information resources and
    red vocabularies.}
  \label{fig:hardtable}
\end{figure}

@@

We find that only one SPARQL endpoint yields a heuristic lifetime, on
closer inspection, we find this to be hosted by
Dydra\footnote{http://dydra.com/}. We speculate that this is due to
that few underlying DBMS systems help track modification times in a
way that can be used on a SPARQL result basis.

@@

For SPARQL endpoints, it is interesting to examine the queries in a
shared proxy, e.g. an institutional cache or a Content
Delivery Network for frequent subpatterns, and prefetch and cache such
intermediate results so that subsequent queries can be answered in
part by the proxy.
